% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
\usepackage{graphicx}
\usepackage{latexsym} 
\usepackage{fancyhdr}
\usepackage{wrapfig}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{biblio.bib}
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

%\renewcommand{\familydefault}{\sfdefault}
\usepackage{times}

\begin{document} 

\begin{center}
\moveleft0.5\hoffset\centerline{\bf {\large Curriculum Vitae} \hspace{11.3cm}
{\large  Deep Ray}}
\end{center}
\vspace{-1cm}
%\moveleft.5\hoffset\centerline{\large\bf Curriculum Vitae}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip 

 
\begin{resume} 
 
%\section{Name}
%Deep Ray

%\section{Date of Birth}
%1st July, 1989

\vspace{-0.5cm}

\section{Current \\ Affiliation}
Department of Computational and Applied Mathematics (CAAM)  \\ Rice University \\ 6100 Main St., Houston, TX 77005 \\
E-mail: deep.ray@rice.edu\\
Webpage: deepray.github.io
 
\section{Employment}
{\it Postdoctoral researcher}, CAAM, Rice University
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item 
July, 2019 to present
\item Involved in the development high-resolution numerical methods to simulate multiphase flows through real rock structures at the pore scale.  
\end{itemize}

{\it Postdoctoral researcher}, MCSS, EPFL
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item 
July, 2017 to June 2019
\item Involved in the development of machine learning strategies to resolve existing bottle-necks in numerical methods.  
\end{itemize}

\section{Education}
{\it Ph.D. in Mathematics}, Tata Institute of Fundamental Research (TIFR-CAM)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item September, 2013 to May, 2017
 \item Advisors: Dr. Praveen Chandrashekar (TIFR-CAM) and Prof. Siddhartha Mishra (ETH Z\"{u}rich and adjunct faculty TIFR-CAM)
  \item Developed and analysed a high-order entropy stable parallelized finite volume solver for the compressible Euler and Navier-Stokes equations on unstructured meshes. 
  \item \textbf{Awarded} the Harish Chandra Memorial Award for the best Ph.D. thesis.
      
 \end{itemize}

 {\it M.Phil in Mathematics}, TIFR-CAM
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item July, 2012 to September, 2013
 \item Advisor: Dr. Praveen Chandrashekar
 \item Worked on numerical schemes for the Euler and Navier-Stokes Equations that preserve entropy, kinetic-energy and vorticity, and performed multi-dimensional simulations for the same.
 \end{itemize}

 {\it M.Sc in Mathematics}, TIFR-CAM
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item August, 2010 to May, 2012
 %\item Cumalative score: 82.37 $\%$
 \end{itemize}
 
 {\it B.Sc (Honours) in Mathematics}, Hindu College, University of Delhi
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item July, 2007 to June, 2010
% \item Cumalative score: 83.89 $\%$
 \end{itemize}
 
% {\it All India Senior School Certificate Examination}, Delhi Public School, R.K. Puram, Delhi
% \begin{itemize} \itemsep -2pt  % reduce space between items
% \item Date: May, 2007
% \item Score: 93.00 $\%$
% \end{itemize} 
% 
% {\it All India Secondary School Certificate Examination}, Delhi Public School, R.K. Puram, Delhi
% \begin{itemize} \itemsep -2pt  % reduce space between items
% \item Date: May, 2005
% \item Score: 89.20 $\%$
% \end{itemize}  

\section{Research \\ Visits}
 {\it Visiting Research Student}, Seminar for Applied Mathematics, ETH Z\"{u}rich
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item May to October, 2014 and August 2015 to May 2016            
 \item Visited Prof. Siddhartha Mishra to work with him and his research group.
 \end{itemize}
 
 \newpage

 \section{Publications}

\textbf{Publication in Journals}                
            \begin{itemize}            
            
            \item {\it Non-intrusive reduced order modelling of unsteady flows using artificial neural networks with application to a combustion problem.} \\
              Q. Wang, J. S. Hesthaven and D.Ray.\\
              Journal of Computational Physics, Vol. 384, pp 289-307 (2019).
            
           \item {\it An artificial neural network as a troubled-cell indicator.}\\
            D. Ray and J. S. Hesthaven.\\
            Journal of Computational Physics, Vol. 367 (15), pp 166-191 (2018).

            \item {\it An entropy stable finite volume scheme for the two dimensional Navier-Stokes equations on triangular grids.}\\
            D. Ray and P. Chandrashekar.\\
             Applied Mathematics and Computation, Vol. 314, pp. 257-286 (2017).

             \item {\it Convergence of fully discrete schemes for diffusive-dispersive conservation laws with discontinuous flux.}\\
              U. Koley, R, Dutta and D. Ray. \\
              ESAIM: Mathematical Modelling and Numerical Analysis, Vol. 50(5), pp.1289-1331, (2016).
              
              \item {\it Entropy stable schemes on two-dimensional unstructured grids for Euler equations.}\\
              D. Ray, P. Chandrashekar, U. S. Fjordholm, S. Mishra. \\
              Communications in Computational Physics, Vol. 19(5), pp. 1111-1140, (2016).
            
              \item {\it A sign preserving WENO reconstruction method.}\\
              U. S. Fjordholm, D. Ray. \\
              Journal of Scientific Computing, Vol. 68(1), pp. 42-63, (2015).
             
              \item {\it Entropy stable schemes for compressible Euler equations.}\\
              D. Ray and P. Chandrashekar.\\
              Int. J. Numer. Anal. Model. Ser. B, no. 4, p. 335-352 (2013).
             \end{itemize}



\textbf{Publication in Conference Proceedings}                
            \begin{itemize}           
              \item {\it A Third-Order Entropy Stable Scheme for the Compressible Euler Equations.}\\
              D. Ray.\\
              Theory, Numerics and Applications of Hyperbolic Problems II. HYP 2016. Springer Proceedings in Mathematics and Statistics, vol 237., 2018

              \item {\it Kinetic energy preserving and entropy stable finite volume schemes for compressible Euler and Navier-Stokes equations.}\\
              D. Ray and P. Chandrashekar.\\
              14th Annual CFD Symposium - Aeronautical Society of India, IISc, Bangalore, 10-11 August, 2012.
             \end{itemize}

\textbf{Submitted for publication}                
            \begin{itemize}           
              
              \item {\it Constraint-Aware Neural Networks for Riemann Problems}. (submitted, 2019) \\
               J. Magiera, D. Ray, J. S. Hesthaven, C. Rohde.
               
               \item {\it Deep learning observables in computational fluid dynamics}. (submitted, 2019) \\
               K. O. Lye, S. Mishra and D. Ray.
               
               \item {\it Controlling oscillations in high-order Discontinuous Galerkin schemes using artificial viscosity tuned by neural networks}. (submitted, 2019) \\
               N. Discacciati, J. S. Hesthaven and D. Ray.
              
              \item {\it Detecting troubled-cells on two-dimensional unstructured grids using a neural network}. (submitted, 2018) \\
               D. Ray and J. S. Hesthaven.
           
              \item {\it Multi-level Monte Carlo finite difference methods for fractional conservation laws with random data.} (submitted, 2018)\\
              U. Koley, D. Ray and T. Sarkar.

             \end{itemize}

             
\section{Talks \\and \\Posters}
  
               {\it Deep learning enhancements of numerical methods} (9th September, 2019)\\
              CAAM Colloquium, Rice University, Houston.
              
              {\it Using deep learning to overcome algorithmic bottlenecks} (18th June, 2019)\\
              \textbf{Invited speaker} at NumHyp 2019, Malaga.
              
              {\it Detecting discontinuities using deep learning} (12th April, 2019)\\
              Deep Learning Meetup, Z\"{u}rich.
                         
             {\it Controlling oscillations in high-order accurate methods through artificial neural networks} (28th February, 2019)\\
              SIAM-CSE 2019, Spokane.
              
              {\it A fully-discrete kinetic energy preserving and entropy conservative scheme for compressible flows} (27th February, 2019)\\
              SIAM-CSE 2019, Spokane.
              
              {\it Controlling spurious oscillations in high-order methods through deep neural networks} (9th January, 2019)\\
              TIFR-CAM Colloquium, Bangalore.
              
               {\it Controlling spurious oscillations in high-order methods through deep neural networks} (15th November, 2018)\\
              High-Fidelity Industrial LES/DNS symposium, Brussels.
             
              {\it An artificial neural network as a troubled-cell indicator} (10th July, 2018)\\
              SIAM Annual Meeting 2018, Portland.
              
               {\it Using neural nets to detect discontinuities} (19th June, 2018)\\
              MATHICSE Retreat, St. Croix.
              
              {\it An artificial neural network for detecting discontinuities} (11th March, 2018)\\
              7th International Conference on High Performance Scientific Computing, Hanoi. 
              
              {\it An artificial neural network for detecting discontinuities} (3rd January, 2018)\\
              TIFR-CAM Colloquium, Bangalore.
              
              {\it A high-resolution energy preserving method for the rotating shallow water equation} (27th September, 2017)\\
               European Conference on Numerical Mathematics and Advanced Applications, Voss.
              
              {\it A third order entropy stable scheme for the compressible Euler equations} (4th August, 2016)\\
               XVI International Conference on Hyperbolic Problems (HYP2016), Aachen. 
              
              {\it A sign preserving WENO reconstruction} (23rd November, 2015)\\
               Department of Mathematics, University of W\"{u}rzburg.
              
              {\it A sign preserving WENO reconstruction} (14th August, 2015)\\
              International Conference on Industrial and Applied Mathematics, Beijing.
              
              {\it A sign preserving WENO reconstruction} (11th June, 2015)\\
              Department of Applied Mathematics, University of Washington, Seattle.
              
              {\it Entropy stable schemes for compressible flows on unstructured meshes} (20th December, 2014)\\
               Conference on Computational PDEs, Finite Element Meet, TIFR-CAM.  
              
              {\it Entropy stable schemes for compressible flows on unstructured meshes} (9th November, 2014)\\
               The 5th International Conference on Scientific Computing and Partial Differential Equations, HKBU, Hong Kong.              
             
              Poster: {\it Entropy stable schemes for compressible flows on unstructured meshes} (9th September, 2014)\\
               Workshop on the Analysis and Numerical Approximation of PDEs, ETH Z\"{u}rich.
              
              {\it Entropy stable schemes for compressible flows} (9th July, 2014)\\
               Department of Mathematics, University of W\"{u}rzburg.             

\section{Workshops} 
             \begin{itemize}
             \item {\it Academic Industry Modelling Week}, University of Z\"{u}rich  (9th-13th November, 2015) 
             
              \item{\it Workshop on the Analysis and Numerical Approximation of PDEs}, ETH Z\"{u}rich (8th - 10th September, 2014)
               
               \item{\it CIME-CIRM Workshop on Mathematical Models and Methods for Living Systems}, Levico Terme, Italy (1st - 5th September, 2014)

              \item{\it Workshop on Optimization with PDE constraints}, TIFR-CAM (25th November - 6th December, 2013)
   
               \item{\it Compact course on Discontinuous Galerkin method for time-dependent convection-dominant PDEs, by Prof. Chi-Wang Shu }, TIFR-CAM (4th - 5th July, 2013)
               
               
               \item{\it IFCAM Summer School on Numerics and Control of PDEs}, IISc, Bangalore (22nd July - 2nd August, 2013)
               
               \item{\it CIMPA Summer Research School on Current Trends in Computational Methods for PDEs}, IISc, Bangalore (24th June - 19th July, 2013)
               
               \item{\it Workshop on Theoretical and Computational Aspects of Nonlinear Waves}, \\NPDE-TCA, IIT-Bombay (27th - 31st May, 2013)

               \item{\it Advanced Workshop on Non-Standard Finite Element Methods}, NPDE-TCA, \\IIT Bombay (11th - 15th Febraury, 2013)

               \item{\it Data Assimilation Research Program}, TIFR-CAM (4th - 23rd July, 2011)

               \item{\it Visiting Students' Research Programme}, TIFR Mumbai (15th June - 10th July, 2009)
               \end{itemize}          
            
              
\section{Teaching \\Experience} 
   
               \begin{itemize} \itemsep -2pt
               \item Mini-course on the Application and Implementation of Deep Learning, at TIFR-CAM (January, 2019).
               \item Teaching Assistant for graduate course on Numerical Methods for Conservation Laws, at EPFL (September - December, 2018)
                \item Teaching Assistant for graduate course on Numerical Methods for Conservation Laws, at EPFL (September - December, 2017)
               \item Teaching Assistant for graduate course on Computational Partial Differential Equations, at TIFR-CAM (January - May, 2015)
               \item Teaching Assistant for graduate course on Numerical Analysis, at TIFR-CAM  (August - December, 2013) 
               \item Teaching Assistant for graduate course on Numerical Analysis, at TIFR-CAM   (August - December, 2012)
               \end{itemize}          
               
\section{Mentoring Experience} 
               
                  \textbf{Master thesis co-supervision:}
                      \begin{table}[!h]
                       \begin{tabular}{llll}
                       Niccol\`{o} Discacciati & EPFL/Politecnico di Milano & 2018 & Curr: PhD, EPFL \\
                       Andrea Romani       & EPFL/Politecnico di Milano & 2019 & Completed                 \\
                       Lukas Schwander    & ETH                                         &  2019 &  Completed             
                        \end{tabular}
                        \end{table}
                        
                     \textbf{Bachelors thesis co-supervision:}
                      \begin{table}[!h]
                       \begin{tabular}{llll}
                       Moritz Reinders \ \ \ &  ETH                  \hspace{3.55cm}                       &  2019 &  Ongoing             
                        \end{tabular}
                        \end{table}   
                                    

\section{Service} 
               \begin{itemize} \itemsep -2pt
               \item Led an interactive session on applied mathematics for high-school students visiting Rice University (July 2019). 
                \item Organised numerical sessions for optimal control at the IFCAM Summer School on Numerics and Control of PDEs-2013, at the Indian Institute of Science, Bangalore.
               \item Organiser of the Students Seminar Series (S$^3$) at TIFR-CAM (2012 - 2013). The purpose of this committee was to organise and oversee talks by motivated students, on mathematical or other science oriented topics.   
               \item General Secretary of the mathematics society ALPHA at Hindu College (2008 - 2009). 
               \item Founding member of {\it Science Forum} at Hindu College (2008-2010). The mandate of this society was to bring together the students from various science departments, so that they could share the knowledge gathered in their respective fields and gain insights into other associated areas.
               \item Founding member of {\it Caucus} at Hindu College (2009-2010). The society served as a forum for discussing various burning national and global issues, and training students for the Model United Nations Co	 nferences.
               \end{itemize}                    
               
\section{Review \\for \\Journals}  
              Journal of Computational Physics (JCP), SIAM Journal on Numerical Analysis (SINUM), SIAM Journal on Scientific Computing (SISC), Communications in Computational Physics (CICP), Journal of Scientific Computing (JOMP), Proceedings of the Royal Society A (RSPA), Computers \& Fluids, BIT Numerical Mathematics (BITN), Indian Journal of Pure and Applied Mathematics (IJPA).
               
               
\section{Computing \\ Skills}
   \begin{tabular}{l p{3in}}
    {\bf Languages:} & C++, Fortran, Python \\

    {\bf Programming Software:} &  MATLAB \\
    
    {\bf Visualisation Software:} & Paraview, Gnuplot, VisIt, Gmsh \\
    
    {\bf Machine-Learning Software:} & TensorFlow
 \end{tabular}


\end{resume} 


\vfill
\begin{flushright}
\textit{Last updated on \today}
\end{flushright}
\end{document} 



